% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[11pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Christine J. Tang}{July 4, 1998}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:chrisjtang98.at.gmail.dot.com}{chrisjtang98\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller(973) 960-2295\sbull
\href{https://github.com/chris-j-tang}{github.com/chris-j-tang}\sbull
\href{https://www.linkedin.com/in/chris-j-tang/}{linkedin.com/in/chris-j-tang}
% \\
% 32 Haran Circle\sbull
% Millburn, NJ\sbull
% 07041

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Personal Statement here.}
% \\
% \\
% Biography
\end{multicols}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://rpi.edu/}{Rensselaer Polytechnic Institute}}
  {\textsc{Troy, NY}} {%
  \headedsubsection
    {Computer Science, Math (BSc) -- \textnormal{~Economics Minor} -- 3.8/4.0}
    {May 2019} {\\}
}

\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{http://www.hass.rpi.edu/pl/hass-research-facilities/?objectID=10049}{\acr{Language Endowed Intelligent Agents Laboratory}}}
    {\textsc{Troy, NY}} {%
    \headedsubsection
      {Research Assistant \& System Administrator}
      {February \apo17 -- present}
      {\bodytext{
        \renewcommand\labelitemi{{\boldmath$\cdot$}}
        \begin{itemize}
          \item Implemented Ubuntu Linux server data migration remotely using Bash shell to better distribute server payload, increase server security, and expand storage space
          \item Worked with senior sysadmins to reimage corrupted central server from backups 
          \item Installed 
          \item Configured bash scripts to automatically restart laboratory's tools on server restarts
        \end{itemize}
      }}
  }
  
\headedsection
  {\href{http://coling2018.org}{\acr{27th International Conference on Computational Linguistics 2018}}}
  {\textsc{Santa Fe, NM}} {%
  \headedsubsection
    {Webmaster}
    {April \apo17 -- present}
    {\bodytext{Filler}}
}

\headedsection
  {\href{http://www.hoppinger.com}{Hoppinger}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Head of Technology}
    {Apr \apo12 -- Oct \apo16}
    {\bodytext{Hoppinger is an open source minded \emph{full-service} internet agency.  In charge of the dev't capacity, reporting directly to managing director and co-founder Marijn Bom.  Drafted and carried out the technical company vision.  Inspired both devs and management to look beyond \acr{PHP}. Grew custom app dev't into a serious revenue segment.  Implemented continuous delivery. Created and taught several in-house courses.  Enacted testing strategy.  Recruited viciously, in part by organizing educational events.  Restructured to fixed team configurations.  Introduced DevOps (Puppet).  Helped to set up the \textit{Customer Support} and \textit{IT ops} dep'ts.  Contributed to the sales pitches for, and in charge of the software architecture for, all technically challenging projects. Involved with many company-wide process improvements.}}
}

%\headedsection
%  {LIP Automatisering}
%  {\textsc{Breda, The Netherlands}} {%
%  \headedsubsection
%    {Software Auditor}
%    {Sep \apo06}
%    {\bodytext{Audited their flag ship product \emph{\acr{LIP} Suite}:\ an %\acr{ERP} solution for construction companies.}}
%}

\headedsection
  {
    \href{http://www.thehealthagency.com}{The Health Agency}
    \acr{(now \href{http://www.minddistrict.com}{MindDistrict})}
  }
  {\textsc{Delft \& Rotterdam, The Netherlands}} {%

  \headedsubsection
    {Software Engineer}
    {Jun \apo05 -- Feb \apo06}
    {\bodytext{Worked on their \acr{CMS} (written in Python and uses Postgre\acr{SQL}, \acr{XML}/\acr{XSLT} and Twisted).}}

  \headedsubsection
    {Software Auditor}
    {Dec \apo06}
    {\bodytext{Assessed their Python/Zope/\acr{Z}o\acr{DB}-based product re-engineering effort.}}
  }

% \vspace{-0.2em}
% \begin{center}
%   \emph{\small Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{Cies' LinkedIn profile} for a more complete list of work experience along with recommendations.}
% \end{center}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Leading and recruiting teams of software engineers.  Big fan of Agile methodologies, continuous delivery and functional programming.  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP~and Haskell.  Solid knowledge of the full web technology stack.  Able to architect \textit{and} implement distributed/\acr{HA} systems.  Strong Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with virtualization/containerization (Docker/Kubernetes, \acr{KVM}, Xen and several \acr{AWS} solutions) and DevOps (Puppet).  Emacs user.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Dutch \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(limited working proficiency)}, French \emph{(elementary proficiency)} and Mandarin Chinese \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}


\end{document}

